Identifying the L1 of non-native writers: the CMU-Haifa system\\[1em] {\large Yulia Tsvetkov$^\ast$\ Naama Twitto$^\dagger$\ Nathan Schneider$^\ast$\ Noam Ordan$^\dagger$\\ Manaal Faruqui$^\ast$\ Victor Chahuneau$^\ast$\ Shuly Wintner$^\dagger$ \ Chris Dyer$^\ast$}\\[-3em]

### 2013-04-13 paper/paper.tex
fixes

% Author comments
\usepackage{color}
\usepackage{bm}
\definecolor{orange}{rgb}{1,0.5,0}
\definecolor{mdgreen}{rgb}{0,0.6,0}
\definecolor{dkblue}{rgb}{0,0,0.5}
\definecolor{dkgray}{rgb}{0.3,0.3,0.3}
\definecolor{slate}{rgb}{0.25,0.25,0.4}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{purple}{rgb}{0.7,0,1.0}
\newcommand{\ensuretext}[1]{#1}
\newcommand{\cjdmarker}{\ensuretext{\textcolor{green}{\ensuremath{^{\textsc{CJ}}_{\textsc{D}}}}}}
\newcommand{\nssmarker}{\ensuretext{\textcolor{magenta}{\ensuremath{^{\textsc{NS}}_{\textsc{S}}}}}}
\newcommand{\swmarker}{\ensuretext{\textcolor{red}{\ensuremath{^{\textsc{S}}_{\textsc{W}}}}}}
\newcommand{\ytmarker}{\ensuretext{\textcolor{blue}{\ensuremath{^{\textsc{Y}}_{\textsc{T}}}}}}
\newcommand{\ntmarker}{\ensuretext{\textcolor{green}{\ensuremath{^{\textsc{N}}_{\textsc{T}}}}}}
\newcommand{\arkcomment}[3]{\ensuretext{\textcolor{#3}{[#1 #2]}}}
%\newcommand{\arkcomment}[3]{}
\newcommand{\ignore}[1]{}
\newcommand{\cjd}[1]{\arkcomment{\cjdmarker}{#1}{green}}
\newcommand{\nss}[1]{\arkcomment{\nssmarker}{#1}{magenta}}
\newcommand{\sw}[1]{\arkcomment{\swmarker}{#1}{red}}
\newcommand{\yt}[1]{\arkcomment{\ytmarker}{#1}{blue}}
\newcommand{\nt}[1]{\arkcomment{\ntmarker}{#1}{orange}}
\newcommand{\w}{\mathbf{w}}
\newcommand{\g}{\mathbf{g}}
\newcommand{\f}{\mathbf{f}}
\newcommand{\x}{\boldsymbol{x}}
\newcommand{\y}{\boldsymbol{y}}
\newcommand{\cost}{c}

@@

\begin{compactdesc}
\item[\feat{DocLen}] Document length in tokens.
\item[\feat{Punct}] Counts of each punctuation mark. 
\item[\feat{Pron}] Counts of each pronoun.
\item[\feat{Position}] Positional token frequency. We use the counts
  for the first two and last three words before the period in each
  sentence as features. High-weight features for the \emph{second} word include: {\tt ARA:2<,>}; {\tt CHI:2<is>}; {\tt HIN:2<can>}.
\item[\feat{PsvRatio}] The proportion of passive verbs out of all
  verbs.
\item[\feat{CxtFxn}] Contextual function words. \raggedright High-weight features include: {\tt CHI:<some JJ>}; \mbox{\tt HIN:<as VBN>}. 
\item[\feat{Misspell}] Spelling correction edits. Features included substitutions, deletions, insertions, doubling of letters and missing doublings of letters, and splittings (\textnl{alot}$\rightarrow$\textnl{a lot}), as well as the word position where the error occurred\nss{i.e. beginning, middle, or end?}. \raggedright High-weight features include: {\tt ARA:DEL<e>}, {\tt ARA:INS<e>}, {\tt ARA:SUBST<e>/<i>}; {\tt GER:SUBST<z>/<y>}; {\tt JPN:SUBST<l>/<r>}, {\tt JPN:SUBST<r>/<l>}; {\tt SPA:DOUBLE<s>}, {\tt SPA:MID\_INS<s>}, {\tt SPA:INS<s>}.
\item[\feat{Restore}] Counts of substitutions, deletions and
  insertions of predefined tokens that we restored in the texts. High-weight features include: {\tt CHI:DELWORD<do>}; {\tt GER:DELWORD<on>}; {\tt ITA:DELWORD<be>}  
\end{compactdesc}
\noindent
\Tref{tbl:addfeats} reports the empirical improvement that each of
these brings independently when added to the main features
(\Sref{sec:mainfeats}).

@@

Production of L2 texts, not unlike translating from L1 to L2, involves
a tension between the imposing models of L1 (and the source text), on
the one hand, and a set of cognitive constraints resulting from the
efforts to generate the target text, on the other. The former is
called \emph{interference} in Translation Studies \citep{Toury:1995}
and \emph{interlanguage}\nss{do you mean `transfer'? I think `interlanguage' refers to the L2 as used by a nonnative speaker, and `transfer' from the L1 is one of the influences on interlanguage.} in second language acquisition
\citep{Selinker1972}. \citet{vered:noam:shuly} designed 32 classifiers to test the validity
of the forces acting on translated texts, and found that features sensitive to interference
consistently yielded the best performing classifiers. And indeed, in
this work too, we find fingerprints of the source language are dominant in the
makeup of L2 texts. The main difference, however, between texts translated by
professionals and the texts we address here, is that more often than
not professional translators translate into their mother tongue,
whereas L2 writers write out of their mother tongue by definition. So
interference is ever more exaggerated in this case, for example, also
phonologically \citep{tsur-rappoport:2007:Cognitive-2007}.

>>>>

% Author comments
\usepackage{color}
\usepackage{bm}
\definecolor{orange}{rgb}{1,0.5,0}
\definecolor{mdgreen}{rgb}{0,0.6,0}
\definecolor{dkblue}{rgb}{0,0,0.5}
\definecolor{dkgray}{rgb}{0.3,0.3,0.3}
\definecolor{slate}{rgb}{0.25,0.25,0.4}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{purple}{rgb}{0.7,0,1.0}
\newcommand{\ensuretext}[1]{#1}
\newcommand{\cjdmarker}{\ensuretext{\textcolor{green}{\ensuremath{^{\textsc{CJ}}_{\textsc{D}}}}}}
\newcommand{\nssmarker}{\ensuretext{\textcolor{magenta}{\ensuremath{^{\textsc{NS}}_{\textsc{S}}}}}}
\newcommand{\swmarker}{\ensuretext{\textcolor{red}{\ensuremath{^{\textsc{S}}_{\textsc{W}}}}}}
\newcommand{\ytmarker}{\ensuretext{\textcolor{blue}{\ensuremath{^{\textsc{Y}}_{\textsc{T}}}}}}
\newcommand{\ntmarker}{\ensuretext{\textcolor{green}{\ensuremath{^{\textsc{N}}_{\textsc{T}}}}}}
%\newcommand{\arkcomment}[3]{\ensuretext{\textcolor{#3}{[#1 #2]}}}
\newcommand{\arkcomment}[3]{}
\newcommand{\ignore}[1]{}
\newcommand{\cjd}[1]{\arkcomment{\cjdmarker}{#1}{green}}
\newcommand{\nss}[1]{\arkcomment{\nssmarker}{#1}{magenta}}
\newcommand{\sw}[1]{\arkcomment{\swmarker}{#1}{red}}
\newcommand{\yt}[1]{\arkcomment{\ytmarker}{#1}{blue}}
\newcommand{\nt}[1]{\arkcomment{\ntmarker}{#1}{orange}}
\newcommand{\w}{\mathbf{w}}
\newcommand{\g}{\mathbf{g}}
\newcommand{\f}{\mathbf{f}}
\newcommand{\x}{\boldsymbol{x}}
\newcommand{\y}{\boldsymbol{y}}
\newcommand{\cost}{c}

@@

\begin{compactdesc}
\item[\feat{DocLen}] Document length in tokens.
\item[\feat{Punct}] Counts of each punctuation mark. 
\item[\feat{Pron}] Counts of each pronoun.
\item[\feat{Position}] Positional token frequency. We use the counts
  for the first two and last three words before the period in each
  sentence as features. High-weight features for the \emph{second} word include: {\tt ARA:2<,>}; {\tt CHI:2<is>}; {\tt HIN:2<can>}.
\item[\feat{PsvRatio}] The proportion of passive verbs out of all
  verbs.
\item[\feat{CxtFxn}] Contextual function words. \raggedright High-weight features include: {\tt CHI:<some JJ>}; \mbox{\tt HIN:<as VBN>}. 
\item[\feat{Misspell}] Spelling correction edits. Features included substitutions, deletions, insertions, doubling of letters and missing doublings of letters, and splittings (\textnl{alot}$\rightarrow$\textnl{a lot}), as well as the word position where the error occurred. %\nss{i.e. beginning, middle, or end?} 
\raggedright High-weight features include: {\tt ARA:DEL<e>}, {\tt ARA:INS<e>}, {\tt ARA:SUBST<e>/<i>}; {\tt GER:SUBST<z>/<y>}; {\tt JPN:SUBST<l>/<r>}, {\tt JPN:SUBST<r>/<l>}; {\tt SPA:DOUBLE<s>}, {\tt SPA:MID\_INS<s>}, {\tt SPA:INS<s>}.
\item[\feat{Restore}] Counts of substitutions, deletions and
  insertions of predefined tokens that we restored in the texts. High-weight features include: {\tt CHI:DELWORD<do>}; {\tt GER:DELWORD<on>}; {\tt ITA:DELWORD<be>}  
\end{compactdesc}
\noindent
\Tref{tbl:addfeats} reports the empirical improvement that each of
these brings independently when added to the main features
(\Sref{sec:mainfeats}).

@@

Production of L2 texts, not unlike translating from L1 to L2, involves
a tension between the imposing models of L1 (and the source text), on
the one hand, and a set of cognitive constraints resulting from the
efforts to generate the target text, on the other. The former is
called \emph{interference} in Translation Studies \citep{Toury:1995}
and \emph{transfer} in second language acquisition
\citep{Selinker1972}. \citet{vered:noam:shuly} designed 32 classifiers to test the validity
of the forces acting on translated texts, and found that features sensitive to interference
consistently yielded the best performing classifiers. And indeed, in
this work too, we find fingerprints of the source language are dominant in the
makeup of L2 texts. The main difference, however, between texts translated by
professionals and the texts we address here, is that more often than
not professional translators translate into their mother tongue,
whereas L2 writers write out of their mother tongue by definition. So
interference is ever more exaggerated in this case, for example, also
phonologically \citep{tsur-rappoport:2007:Cognitive-2007}.
